Metabolites reflect variability introduced by mesoscale eddies in the North Pacific Subtropical Gyre

### 2024-07-01 manuscript/manuscript.Rmd
Adding acknowledgements and data availability statements

Although the untargeted pool contains more molecular features, we expect that a majority of the signal has been captured by our 53 targeted compounds. Of the total peak area that passed quality control, approximately 67% was captured by these 53 molecules. An additional 15% of the total peak area was putatively annotated as various inorganic ions for which no authentic standard was available but could be matched by mass and isotope pattern. Additionally, our targeted list accounted for 13 out of the top 20 largest molecular features by total peak area with an additional 4 features annotated as the inorganic ions for 17/20 of the largest features known. However, these calculations should be taken as estimates because peak area does not correspond directly to environmental concentration and it is entirely possible for abundant environmental compounds to have small peak areas if they ionize poorly on the mass spectrometer or degrade during the sampling and extraction process.

@@

>>>>

Although the untargeted pool contains more molecular features, we expect that a majority of the signal has been captured by our 53 targeted compounds. Of the total peak area that passed quality control, approximately 67% was captured by these 53 molecules. An additional 15% of the total peak area was putatively annotated as various inorganic ions for which no authentic standard was available but could be matched by mass and isotope pattern. Additionally, our targeted list accounted for 13 out of the top 20 largest molecular features by total peak area with an additional 4 features annotated as the inorganic ions for 17/20 of the largest features known. However, these calculations should be taken as estimates because peak area does not correspond directly to environmental concentration and it is entirely possible for abundant environmental compounds to have small peak areas if they ionize poorly on the mass spectrometer or are removed during the sampling and extraction process.

@@

# Acknowledgements

The authors would like to thank the other members of the Ingalls Lab who provided assistance in sample processing, integration, and analysis. We are also grateful to the SCOPE science team (Tara Clemente and Tim Burrell) for sample collection during the Hawaiian Eddy Experiment. We would like to acknowledge the captain and crew of the R/V *Kilo Moana* and R/V *Falkor* during the KM1709 and FK180310 cruises for making this science possible. We would also like to acknowledge the analysts involved in the biogeochemical measurements for their willingness to provide data and answer questions (Eric Grabowski, Karin Bjorkman, and Rhea Foreman). This work was supported by grants from the Simons Foundation (SCOPE Award ID 329108 to AI, SF Award ID 385428 to AI).

The authors have no conflicts of interest to declare.

# Data availability

Data and code used for this manuscript are all available online. Biogeochemical data can be sourced from the Simons SCOPE website at https://scope.soest.hawaii.edu/data/ and metabolomics data has been uploaded to Metabolomics Workbench under Project ID PR001738, where the data can be accessed directly via its DOI: 10.21228/M82719. Scripts used to process metabolomics data are available on GitHub at https://github.com/wkumler/MesoscopeMetabolomicsManuscript.
